Sustainable Pathways for Irish homes in changing TIMES

### 2021-07-09 manuscript.tex
Energy Service Demands

\subsubsection{Energy Service Demand Projections}
\label{LitR:Demands}
%JF -The tax / subsidy inclusive prices are important in driving behaviour, and taxes and subsidies will be a vital policy instrument. Thus, uptake of technologies such as retrofitting will be driven, inter alia, by the net price for consumers.
The residential energy service demand projections are a critical component of TIM. The future population projections are obtained from CSO's \textit{``M2F1"} scenario  %\cite{}. 
 .

@@

The residential stock projections up to 2040 are taken from ESRI's housing demand estimates \cite{Bergin2020}. The stock is expected to increase by 40\% from 2018 level with a CAGR of 2\%. This results in an average of 27,600 new houses per annum between between 2021-2040. Beyond 2040, the population is used as a driver to project housing stock. The total housing stock obtained in 2050 is 2.57 million, which implies 8\% increase from 2040. 
% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \footnotesize
  \caption{Number of dwellings by type ('000)}
    \begin{tabular}{rrrr}
    \hline
    \multicolumn{1}{l}{Year} & \multicolumn{1}{l}{Apartment} & \multicolumn{1}{l}{Attached } & \multicolumn{1}{l}{Detached} \\ \hline
    2018  & 207   & 766   & 724 \\
    2030  & 355   & 918   & 833 \\
    2040  & 493   & 1003  & 878 \\
    2050  & 629   & 1057  & 890 \\ \hline
    \end{tabular}%
  \label{tab:addlabel}%
\end{table}%

>>>>

\subsubsection{Energy Service Demand Projections}
\label{LitR:Demands}

Energy service demands in the residential sector are driven by the total dwelling stock for non-archetype energy services or apartment, attached or detached dwelling stock for archetype energy services, which in turn is driven by population growth and the occupancy rate (the average number of people per dwelling). The residential stock projections up to 2040 are taken from Economic and Social Research Institute's (ESRI's) housing demand estimates \cite{BerginREGIONALLEVEL}.
Archetype energy service demands are dependant on both the type of dwelling and whether it is existing or new. The average archetype energy service in new and existing per archetpe is shown in Table X.
\begin{table}[htbp]
  \centering
  \footnotesize
  \caption{Archetype Energy Service Demands}
 \begin{tabular}{c|cc|cc|cc}
 \hline
 \multicolumn{1}{c|}{Energy Service}  & \multicolumn{2}{c|}{Apartments} & \multicolumn{2}{c|}{Attached} & \multicolumn{2}{c}{Detached}  \\

  & Existing & New & Existing & New & Existing & New \\
 \hline
 Space Heating & 2.79 & 81\% & 2.79 & 81\% & 2.79 & 81\% \% \\
 Water Heating & 3.63 & 81\% & 3.63 & 81\% & 3.63 & 81\% \% \\
 Lighting & 7.5 & 307\% & 6.83 & 338\% & 6.21 & 379\%  \\
 Pumps \& Fans  & 3.25 & 82\% & 3.25 & 82\% & 3.25 & 82\%  \\
 Space Cooling  & 4.23 & 82\% & 4.23 & 82\% & 4.23 & 82\%  \\
 \hline
 \end{tabular}

 \label{Archetype Energy Service Demands}
\end{table}
%%PICK UP HERE
TABLE Y - Apartment Growth - 
%% Ask Ankita for more info about Demand Calculations!!
%Compound Annual Growth Rate (CAGR)
%The occupancy rate is expected to fall to 2.12 in 2051 \citep{PropertyIndustryIreland2019}, from 2.75 in 2016 (CSO).

%  Intermediate values are estimated using Equation \ref{eq:OR}.
% \begin{equation}
% \label{eq:OR}
%  OR= a+b*log(\Delta t)
% \end{equation}
% here, $OR$ is the occupancy rate, $\Delta t$ is difference between years, parameters $a$ \& $b$ are estimated using historical values.

 The stock is expected to increase by 40\% from 2018 level with a CAGR of 2\%. This results in an average of 27,600 new houses per annum between between 2021-2040. Beyond 2040, the population is used as a driver to project housing stock. The total housing stock obtained in 2050 is 2.57 million, which implies 8\% increase from 2040. 
% Table generated by Excel2LaTeX from sheet 'Sheet1'
\begin{table}[htbp]
  \centering
  \footnotesize
  \caption{Number of dwellings by type ('000)}
    \begin{tabular}{rrrr}
    \hline
    \multicolumn{1}{l}{Year} & \multicolumn{1}{l}{Apartment} & \multicolumn{1}{l}{Attached } & \multicolumn{1}{l}{Detached} \\ \hline
    2018  & 207   & 766   & 724 \\
    2030  & 355   & 918   & 833 \\
    2040  & 493   & 1003  & 878 \\
    2050  & 629   & 1057  & 890 \\ \hline
    \end{tabular}%
  \label{tab:addlabel}%
\end{table}%

@@
